Faithful Model Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-12-13 paper/camera-ready/altmeyer.tex
sorted out references
tables added in

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

@@

@@

@@

\bibliography{aaai24}

>>>>

\setcounter{secnumdepth}{1} %May be changed to 1 or 2 if section numbers are desired.

@@

\begin{table*}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llcccccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{3}{c}{California Housing} & \multicolumn{3}{c}{GMSC} \\
\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8}
Model & Generator & Unfaithfulness ↓ & Implausibility ↓ & Uncertainty ↓ & Unfaithfulness ↓ & Implausibility ↓ & Uncertainty ↓\\
\midrule
    & ECCCo & \textbf{3.69 ± 0.08}** & 1.94 ± 0.13\hphantom{*}\hphantom{*} & \textbf{0.09 ± 0.01}** & 3.84 ± 0.07** & 2.13 ± 0.08\hphantom{*}\hphantom{*} & \textbf{0.23 ± 0.01}**\\

    & ECCCo+ & 3.88 ± 0.07** & 1.20 ± 0.09\hphantom{*}\hphantom{*} & 0.15 ± 0.02\hphantom{*}\hphantom{*} & \textbf{3.79 ± 0.05}** & 1.81 ± 0.05\hphantom{*}\hphantom{*} & 0.30 ± 0.01*\hphantom{*}\\

    & ECCCo (no CP) & 3.70 ± 0.08** & 1.94 ± 0.13\hphantom{*}\hphantom{*} & 0.10 ± 0.01** & 3.85 ± 0.07** & 2.13 ± 0.08\hphantom{*}\hphantom{*} & 0.23 ± 0.01**\\

    & ECCCo (no EBM) & 4.03 ± 0.07\hphantom{*}\hphantom{*} & 1.12 ± 0.12\hphantom{*}\hphantom{*} & 0.14 ± 0.01** & 4.08 ± 0.06\hphantom{*}\hphantom{*} & 0.97 ± 0.08\hphantom{*}\hphantom{*} & 0.31 ± 0.01*\hphantom{*}\\

    & REVISE & 3.96 ± 0.07*\hphantom{*} & \textbf{0.58 ± 0.03}** & 0.17 ± 0.03\hphantom{*}\hphantom{*} & 4.09 ± 0.07\hphantom{*}\hphantom{*} & \textbf{0.63 ± 0.02}** & 0.33 ± 0.06\hphantom{*}\hphantom{*}\\

    & Schut & 4.00 ± 0.06\hphantom{*}\hphantom{*} & 1.15 ± 0.12\hphantom{*}\hphantom{*} & 0.10 ± 0.01** & 4.04 ± 0.08\hphantom{*}\hphantom{*} & 1.21 ± 0.08\hphantom{*}\hphantom{*} & 0.30 ± 0.01*\hphantom{*}\\

\multirow{-7}{*}{\raggedright\arraybackslash MLP Ensemble} & Wachter & 4.04 ± 0.07\hphantom{*}\hphantom{*} & 1.13 ± 0.12\hphantom{*}\hphantom{*} & 0.16 ± 0.01\hphantom{*}\hphantom{*} & 4.10 ± 0.07\hphantom{*}\hphantom{*} & 0.95 ± 0.08\hphantom{*}\hphantom{*} & 0.32 ± 0.01\hphantom{*}\hphantom{*}\\
\cmidrule{1-8}
    & ECCCo & 1.40 ± 0.08** & 0.69 ± 0.05** & 0.11 ± 0.00** & 1.20 ± 0.06*\hphantom{*} & 0.78 ± 0.07** & 0.38 ± 0.01\hphantom{*}\hphantom{*}\\

    & ECCCo+ & \textbf{1.28 ± 0.08}** & 0.60 ± 0.04** & 0.11 ± 0.00** & \textbf{1.01 ± 0.07}** & 0.70 ± 0.07** & 0.37 ± 0.01\hphantom{*}\hphantom{*}\\

    & ECCCo (no CP) & 1.39 ± 0.08** & 0.69 ± 0.05** & 0.11 ± 0.00** & 1.21 ± 0.07*\hphantom{*} & 0.77 ± 0.07** & 0.39 ± 0.01\hphantom{*}\hphantom{*}\\

    & ECCCo (no EBM) & 1.70 ± 0.09\hphantom{*}\hphantom{*} & 0.99 ± 0.08\hphantom{*}\hphantom{*} & 0.14 ± 0.00*\hphantom{*} & 1.31 ± 0.07\hphantom{*}\hphantom{*} & 0.97 ± 0.10\hphantom{*}\hphantom{*} & 0.32 ± 0.01**\\

    & REVISE & 1.39 ± 0.15** & \textbf{0.59 ± 0.04}** & 0.25 ± 0.07\hphantom{*}\hphantom{*} & 1.01 ± 0.07** & \textbf{0.63 ± 0.04}** & 0.33 ± 0.07\hphantom{*}\hphantom{*}\\

    & Schut & 1.59 ± 0.10*\hphantom{*} & 1.10 ± 0.06\hphantom{*}\hphantom{*} & \textbf{0.09 ± 0.00}** & 1.34 ± 0.07\hphantom{*}\hphantom{*} & 1.21 ± 0.10\hphantom{*}\hphantom{*} & \textbf{0.26 ± 0.01}**\\

\multirow{-7}{*}{\raggedright\arraybackslash JEM Ensemble} & Wachter & 1.71 ± 0.09\hphantom{*}\hphantom{*} & 0.99 ± 0.08\hphantom{*}\hphantom{*} & 0.14 ± 0.00\hphantom{*}\hphantom{*} & 1.31 ± 0.08\hphantom{*}\hphantom{*} & 0.95 ± 0.10\hphantom{*}\hphantom{*} & 0.33 ± 0.01\hphantom{*}\hphantom{*}\\
\bottomrule
\end{tabular}}
\caption{Results for tabular datasets: sample averages +/- one standard deviation across valid counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (\textit{Wachter}). \label{tab:results-tabular}}
\end{table*}

@@

\begin{table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llcc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{2}{c}{MNIST} \\
\cmidrule(l{3pt}r{3pt}){3-4}
Model & Generator & Unfaithfulness ↓ & Implausibility ↓\\
\midrule
    & ECCCo & \textbf{0.243 ± 0.000}** & 0.420 ± 0.001\hphantom{*}\hphantom{*}\\

    & ECCCo+ & 0.246 ± 0.000*\hphantom{*} & 0.306 ± 0.001**\\

    & REVISE & 0.248 ± 0.000\hphantom{*}\hphantom{*} & \textbf{0.301 ± 0.004}**\\

    & Schut & 0.247 ± 0.001\hphantom{*}\hphantom{*} & 0.303 ± 0.008**\\

\multirow{-5}{*}{\raggedright\arraybackslash MLP} & Wachter & 0.247 ± 0.000\hphantom{*}\hphantom{*} & 0.344 ± 0.002\hphantom{*}\hphantom{*}\\
\cmidrule{1-4}
    & ECCCo & 0.248 ± 0.000** & 0.387 ± 0.002\hphantom{*}\hphantom{*}\\

    & ECCCo+ & \textbf{0.248 ± 0.000}** & 0.310 ± 0.002**\\

    & REVISE & 0.248 ± 0.000** & 0.301 ± 0.002**\\

    & Schut & 0.250 ± 0.002\hphantom{*}\hphantom{*} & \textbf{0.289 ± 0.024}*\hphantom{*}\\

\multirow{-5}{*}{\raggedright\arraybackslash LeNet-5} & Wachter & 0.249 ± 0.000\hphantom{*}\hphantom{*} & 0.335 ± 0.002\hphantom{*}\hphantom{*}\\
\bottomrule
\end{tabular}}
\caption{Results for vision dataset. Formatting details are the same as in Table~\ref{tab:results-tabular}. \label{tab:results-vision}}
\end{table}

@@

\bibliography{aaai24,bib}
